Visual Interrogation of Attention-Based Models: \\ Applications in Language Inference and Machine Comprehension

### 2018-05-27 EMNLP-demo-paper/intro.tex
add abstract
update intro
add figure

Neural networks have been successful in various natural language processing tasks,
where end-to-end training become a primary option (\cite{}).
As the design of neural networks evolve, there is a clear trend that more and more
parameters participate in training and prediction. While the strong expressivity
enhance model performance, the lack of interpretability presents challenge for analysis.
Without understanding the background meaning that features carry, visualization relies
on proper quantification analysis (cite). Such analysis is not easy to come up with,
and is tied to specific task (cite).

@@

In summary, our contribution in this papers are:
\begin{itemize}
	\item 1. We present an interactive visualization system for word-attention neural
	networks in NLP. Our system allows to...
	\item 2. We demonstrate our system on two major NLP tasks with strong-performing
	models. We observe functional limitations of these models which can be helpful
	for future improvement on modeling.
\end{itemize}

exploration task

Comparsion with AllenNLP

>>>>

Neural networks have been successful in various natural language processing tasks,
where end-to-end training become a primary option \cite{Seo2016}.
As the design of neural networks evolve, there is a clear trend that more and more
parameters participate in training and prediction. While the strong expressivity
enhance model performance, the lack of interpretability presents challenge for analysis.
Without understanding the background meaning that features carry, visualization relies
on proper quantification analysis (cite). Such analysis is not easy to come up with,
and is tied to specific task (cite).

@@

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{pipeline}
 \caption{
 Perturbation-Driven Exploration of the NLP Model.
 }
\label{fig:modelPipeline}
\end{figure}

In summary, our key contributions are:
\begin{itemize}
	\item Introduce an flexible visualization system for creating customized interactive visual analytic environment for attention centric neural networks model in NLP. 
	\item Illustrate the importance of streamlining the query to the model
	\item Demonstrate our system on two major NLP tasks with strong-performing
	models. We observe functional limitations of these models which can be helpful
	for future improvement on modeling.
\end{itemize}

exploration task
\cite{Seo2016}
Comparsion with AllenNLP
